GBDCompare

### 2018-04-17 MSLT/GBDCompare.Rmd
GBD COmpare to html
Add options to set messages and warnings to false

---
title: "GBDCompare"
author: "Belen Zapata Diomedi"
date: "17 April 2018"
output: pdf_document
---

@@

```{r, echo = FALSE}
###TO DO: cubic splines for input rates

>>>>

---
title: "GBDCompare"
author: "Belen Zapata Diomedi"
date: "17 April 2018"
output: html_document
---

@@

```{r, echo = FALSE, message=FALSE, warning=FALSE}
###TO DO: cubic splines for input rates
